The Transition from Massive Metal Free Stars to Dwarf Galaxies

### 2011-02-22 ms.tex
Making the combination model the primary model.  Need to change all results once the simulation is finished.

We perform nine different simulations with the same initial
conditions.  The fiducial model considers (a) primordial cooling with
9 species of hydrogen, helium, and molecular hydrogen, (b) a Pop III
IMF characteristic mass $M_{\rm char}$ = 100 \Ms, (c) Pop II and Pop
III star formation, and (d) a critical metallicity of [Z/H] = --4.  We
vary this model with the following changes:

\begin{enumerate}
\item Additional radiative cooling from metal species.  We calculate a
  cooling curve with CLOUDY \citep{CLOUDY} and use the method of
  \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
  cooling curve.  It is tabulated based on density, temperature,
  electron fraction, and total metallicity.
\item A critical metallicity of [Z/H] = --5 and --6, accounting for
  the case where dust cooling can induce low-mass fragmentation in
  these lower metallicities \citep{Omukai05, Schneider06_Frag}.
\item Higher Pop II metal yield of $y = 0.025$ that is consistent with
  average values in the Milky Way \citep{Madau96}.
\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
  the abundance patterns of EMP stars and reionization as constaints,
  the data are best fit with IMFs favoring stars with masses between
  20--130 \Ms~\citep{Umeda03, Tumlinson06}.
\item Lyman-Werner radiation background.  We use the semi-analytical
  model of \citet{Wise05}, updated with the 7-year WMAP parameters and
  optical depth to Thompson scattering, to calculate the LW background
  intensity, plotted in Fig. \ref{fig:uvb}.  In this semi-analytical
  model, we use a Pop III stellar mass of 100 \Ms, star formation
  efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
  LW radiation from point sources are added to the background.  The
  intensity decreases after $z \sim 14$ because Pop II star formation
  becomes dominant, which produce less LW specific luminosity than Pop
  III stars that have surface temperatures of $T = 10^5$ K.  For
  computational convenience, we fit the background evolution with the
  function
%
  \begin{equation}
    \label{eqn:uvb}
    \log_{10} J_{21}(z) = A + Bz + Cz^2 + Dz^3 + Ez^4,
  \end{equation}
%
  where $(A,B,C,D,E) = (-2.356, 0.4562, -0.02680, 5.882 \times 10^{-4},
  -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
  units of $10^{-21}$ \emis.  This fits the
  model data within 1\% in $6 \le z \le 30$ and is consistent with
  $J_{21}$ values in \citet{Trenti09_SFR}.
\item Pop II star formation only.  This model is useful to study the
  importance of treating Pop III star formation as single stars and
  their pair-instability and Type II SNe.
\item Pop II star formation only and no molecular hydrogen cooling.
  This model provides a good comparison to larger scale simulations
  where it is not computationally feasible to consider \hh~cooling or
  resolve the necessary scales for Pop III star formation.
\end{enumerate}

@@

Here we present the gaseous and stellar evolution of the high-redshift
dwarf galaxies that form in our simulations.  To illustrate its global
properties, we show the density-weighted projections of gas density,
temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
Fig. \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of IGM
over this redshift range, where the mass- and volume-averaged ionized
fraction are 0.431 and 0.417 at $z=7$, respectively.  The metallicity
projections show the growth of metal-enriched bubbles, starting first
with enrichment from Pop III stars.  Then as time progresses, the
haloes enriched within these bubbles above $Z_{\rm cr}$ transition to
Pop II star formation, enriching their host halo and surrounding IGM.
In Fig. \ref{fig:mass_fn}, we show the halo mass function, agreeing
well with the analytic halo mass function of \citet{Warren06}.  We
identify the haloes with a friends-of-friends (FOF) algorithm
\citep{Davis85}.  The excess of low-mass haloes below $M_{\rm DM} = 2
\times 10^6 \Ms$ is most likely associated with the biased region in
the lower-right region in the projections.  Furthermore, the
uncertainities in different analytic halo mass functions
\citep[see][for a comparison]{Reed07} and halo identification are
comparable than these differences.  Our fidicual model contains 38
galaxies with a total of 3640 Pop II star clusters and captures the
formation of 333 Pop III stars.

>>>>

We perform ten different simulations with the same initial conditions.
The baseline model considers (a) primordial cooling with 9 species of
hydrogen, helium, and molecular hydrogen, (b) a Pop III IMF
characteristic mass $M_{\rm char}$ = 100 \Ms, (c) Pop II and Pop III
star formation, and (d) a critical metallicity of [Z/H] = --4.  We
vary this model with the following changes:

\begin{enumerate}
\item Additional radiative cooling from metal lines.  We calculate a
  cooling curve with CLOUDY \citep{CLOUDY} and use the method of
  \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
  cooling curve.  It is tabulated based on density, temperature,
  electron fraction, and total metallicity.
\item A critical metallicity of [Z/H] = --5 and --6, accounting for
  the case where dust cooling can induce low-mass fragmentation in
  these lower metallicities \citep{Omukai05, Schneider06_Frag}.
\item Higher Pop II metal yield of $y = 0.025$ that is consistent with
  average values in the Milky Way \citep{Madau96}.
\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
  the abundance patterns of EMP stars and reionization as constaints,
  the data are best fit with IMFs favoring stars with masses between
  20--130 \Ms~\citep{Umeda03, Tumlinson06}.
\item Lyman-Werner radiation background.  We use the semi-analytical
  model of \citet{Wise05}, updated with the 7-year WMAP parameters and
  optical depth to Thompson scattering, to calculate the LW background
  intensity, plotted in Fig. \ref{fig:uvb}.  In this semi-analytical
  model, we use a Pop III stellar mass of 100 \Ms, star formation
  efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
  LW radiation from point sources are added to the background.  The
  intensity decreases after $z \sim 14$ because Pop II star formation
  becomes dominant, which produce less LW specific luminosity than Pop
  III stars that have surface temperatures of $T = 10^5$ K.  For
  computational convenience, we fit the background evolution with the
  function
%
  \begin{equation}
    \label{eqn:uvb}
    \log_{10} J_{21}(z) = A + Bz + Cz^2 + Dz^3 + Ez^4,
  \end{equation}
%
  where $(A,B,C,D,E) = (-2.356, 0.4562, -0.02680, 5.882 \times 10^{-4},
  -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
  units of $10^{-21}$ \emis.  This fits the
  model data within 1\% in $6 \le z \le 30$ and is consistent with
  $J_{21}$ values in \citet{Trenti09_SFR}.
\item Pop II star formation only.  This model is useful to study the
  importance of treating Pop III star formation as single stars and
  their pair-instability and Type II SNe.
\item Pop II star formation only and no molecular hydrogen cooling.
  This model provides a good comparison to larger scale simulations
  where it is not computationally feasible to consider \hh~cooling or
  resolve the necessary scales for Pop III star formation.
\item Combination of metal cooling (model i), increased metal yields
  (model iii), a LW background (model v).  This provides the best
  physical scenario for the high-$z$ universe, and we consider it as
  our \textit{primary model}.
\end{enumerate}

@@

Here we present the gaseous and stellar evolution of the high-redshift
dwarf galaxies that form in our \textit{primary physical model} with
metal-line radiative cooling, Pop II metal yields that agree with MW
data, and a LW radiation background.  To illustrate its global
properties, we show the density-weighted projections of gas density,
temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
Fig. \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of IGM
over this redshift range, where the mass- and volume-averaged ionized
fraction are 0.431 and 0.417 at $z=7$, respectively.  The metallicity
projections show the growth of metal-enriched bubbles, starting first
with enrichment from Pop III stars.  Then as time progresses, the
haloes enriched within these bubbles above $Z_{\rm cr}$ transition to
Pop II star formation, enriching their host halo and surrounding IGM.
In Fig. \ref{fig:mass_fn}, we show the halo mass function, agreeing
well with the analytic halo mass function of \citet{Warren06}.  We
identify the haloes with a friends-of-friends (FOF) algorithm
\citep{Davis85}.  The excess of low-mass haloes below $M_{\rm DM} = 2
\times 10^6 \Ms$ is most likely associated with the biased region in
the lower-right region in the projections.  Furthermore, the
uncertainities in different analytic halo mass functions
\citep[see][for a comparison]{Reed07} and halo identification are
comparable than these differences.  Our fidicual model contains 38
galaxies with a total of 3640 Pop II star clusters and captures the
formation of 333 Pop III stars.
